---
title: "Iridescence Untwined Statistical Analysis and Figures"
author: "Authors removed for double blind review"
date: "4/11/2021"
output:
  html_document: 
    toc: yes
    toc_float: yes
    toc_depth: 5
    highlight: tango
    theme: paper
    self_contained: yes
    mode: selfcontained
runtime: shiny
editor_options: 
  
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, echo=FALSE}
knitr::opts_chunk$set(error = TRUE)
```

# Introduction

This document is provided as supplementary information for the manuscript 'Iridescence untwined: Honey bees can separate hue variations in space and time'. 

In our study, we demonstrate the relevance of separately considering the temporal and spatial components of iridescence by showing that our model species, honey bees, can separately attend to one property (temporal) whilst ignoring the other (spatial). Here we include analysis of the spectral curves form our stimulus, visual models and statistical tests for the results of behavioural experiments. 

All code is written in the R programming language unless specifically stated otherwise.

Find the original script and Data here: https://github.com/lospinarozo/Iridescence_Untwined 


# Libraries 



```{r eval=TRUE, message=FALSE, warning=FALSE}

library(pavo) # Spectral curves processing and color models
library(dplyr) # Data wrangling
library(tidyr) # Data wrangling
library(lme4) # For fitting models
library(DHARMa) # For model assumptions
library(ggplot2) # For plotting
library(shiny) # For interactive plots
library(rsconnect) # To obtain HTML from shiny doc

```


# Data

```{r, message=FALSE, warning=FALSE}

# Spectral data - raw

## Iridescent stimulus
IriDataRaw <- read.csv(
  "1.IridescentDisc_RawSpectralData.csv", header=TRUE)
IriData <- as.rspec(IriDataRaw[IriDataRaw$wl <= 700, ])
IriData <- procspec(IriData,  fixneg = "zero")

## Backgrounds
BkgDataRaw <- read.csv(
  "2.GreyBackgrounds_RawSpectralData.csv",header=TRUE) 
BkgData <- as.rspec(BkgDataRaw[BkgDataRaw$wl <= 700 & BkgDataRaw$wl >= 300, ])
BkgData <- procspec(BkgData, fixneg = "zero")

## Distractors
DisDataRaw <- read.csv(
  "3.Distractors_RawSpectralData.csv",header=TRUE)
DisData <- as.rspec(DisDataRaw[DisDataRaw$wl <= 700 & DisDataRaw$wl >= 300,])
DisData <- procspec(DisData, fixneg = "zero")
DisData <- procspec(DisData, opt = "smooth", span = 0.05)

## Blue Stimulus
BlueDataRaw <- read.csv(
  "4.BlueStimulus_RawSpectralData.csv")
BlueData <- as.rspec(BlueDataRaw[BlueDataRaw$wl <= 701 & BlueDataRaw$wl >= 300,])
BlueData <- procspec(BlueData, fixneg = "zero")

# Data for training phase (choices 1-60) 
B_CHOICE <- read.csv("5.BeeChoices_TrainingPhase.csv")  

# Data for unrewarded tests 
B_TEST <- read.csv("6.BeeChoices_TestingPhase.csv")  

# Iridescence Point Illumination
IriPoint <- read.csv("7.IridescentDiscPointIllumination.csv")

```

# Data analysis

## Iridescence Stimulus

### Spectral shift quantification

Spectral characterization of the iridescent stimulus

```{r, results="hide", fig.show='hide'}

# Blue shift calculations

## First create a data frame with the spectral location for each spectrum

ps <- peakshape(IriData) # obtain spectral descriptors

```

This step is convenient to save time and computational power while re-using the parameters extracted from the function `peakshape` without generating the plots each time. 

```{r}
SpecLoc <- ps$H1 - ps$HWHM.l # obtain spectral location
labels <- names(IriData) # Names of each column
Position_light <- substring(labels  [ 2: length(labels)], 1, 3) # Light source
Angle_collector <- substring(labels [ 2: length(labels)], 5, 6) # Collector

Spectral <- data.frame(
  "Position" = Position_light,
  "Angle" = as.numeric(Angle_collector),
  "SpecLoc" = as.numeric(SpecLoc)
) # Data frame with the spectral location 

#Note: In this paper we used a linear model to quantify iridescence
#The slope of the linear model is the shifting of the spectra

## Use a loop to find the slope for each position of the light source
Iridescence <- rep(1,15) # initial empty vector
Position1to15 <- c("P01","P02","P03","P04","P05", "P06",
                   "P07","P08","P09","P10","P11", "P12", 
                   "P13","P14","P15") # positions of the light source
j <- 1 # Accumulator to allow consecutive iterations in the loop
for (i in Position1to15) {
  mod <- lm(Spectral$SpecLoc [Spectral$Position == i]~
             Spectral$Angle  [Spectral$Position == i]) # model each position
  Iridescence [j] <- round(as.numeric(summary(mod)$coefficients[2]), 3) # slope
  j <- j + 1 # repeat for each position
}

## Create a dataframe with the absolute magnitude of the slope (blue shift)
BlueShiftData<-data.frame(
  "Position" = Position1to15,
  "BlueShift" = Iridescence * (-1)
)

## Obtain statistics
summary(BlueShiftData$BlueShift) 
sd(BlueShiftData$BlueShift)

```

### Visualization (Fig.3A) 

Visualization of the blue shift in the iridescent stimulus 

```{r}
# Example with the light in position 9. 


ForP09 <- 
  IriData %>% 
  select (wl, contains ("P09")) %>% 
  gather (Pos, Reflectance, - wl) %>% 
  mutate (Angle = substr(Pos,5,6)) 


ggplot (ForP09, aes(wl, Reflectance)) +
  geom_line(aes(color=Angle), size=0.8) +
  theme_bw() +
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank())+
  theme(legend.title=element_blank())+
  theme(legend.position = c(.99, .99),
        legend.justification = c("right", "top"))+
  ylab("Reflectance (%)")+
  xlab("Wavelength (nm)")+
  scale_color_grey(start = 0, end = 0.75) + 
  theme(legend.text = element_text(size=7))+
  theme(legend.text = element_text(size=7))+
  theme(legend.key=element_blank())+
  theme(legend.key.height = unit(0.4, 'cm'),
        legend.key.width= unit(0.4, 'cm'))
  




```

## Bee colour vision models

### Temporal Component (Fig.3C)


```{r}
# Iridescent stimulus
# Example with the light in position 9. 

## Create the visual models:
bee_modelc <- vismodel((IriData [,c(1,40:45)]), # consider only position 9
                    visual = "apis", achromatic = "l", 
                    illum = "D65", qcatch = "Ei", 
                    bkg = BkgData$GB1_10, # grey background
                    vonkries = T, relative = F) 

## visualize in hex space:
hex_spacec = colspace(bee_modelc, space = "hexagon") # create the hex space
colours1 <- spec2rgb(IriData [,c(1,40:45)]) # Human RGB values
plot(hex_spacec,col = colours1, cex = 1.5) # plot the hex space

# Note: We used human RGB values only for visualization purposes
# But these values are not related to the bee perception of colour

```

### Spatial Component (Fig.3C) 

 

```{r}
# Colourful distractors
# Example modelling distractors 9 and 10

## Create the visual models:
bee_ddc <- vismodel(DisData[,c(1,28:35)], # only distractors 9 and 10
                 visual = "apis", achromatic="l", 
                 illum = "D65", qcatch = "Ei", 
                 bkg = BkgData$GB1_10,  # grey background
                 vonkries = T, relative = F)

## visualize in hex space:
hsddc <- colspace(bee_ddc, space = "hexagon") # create the hex space
colours2 <- spec2rgb(DisData[,c(1,28:35)]) # Human RGB values
plot(hsddc,col= colours2, cex = 1.5) # plot the hex space

# Note: We used human RGB values only for visualization purposes
# Each colour represents a patch in the colorful distractor
# But these values are not related to the bee perception of colour

```

## Bee spatial acuity (Fig. 4 & Fig. S8)

Spatial acuity was simulated using the toBeeView program using the following code structure:

```{r eval= FALSE}

toBeeView -i Filename.png -d 50 -h 50  -r 1.9  -p 1.8
```

Here, the simulation is set to a viewing distance (d) of 50 mm and a height (h) of 50 mm. To generate simulations at 10 cm and 20 cm, we changed 'd' to 100 and 200.


## Bee Behaviour

### Generalized linear models

#### Training phase

```{r message=FALSE}

# Generalized linear model for the training phase

lm1 <- glm(CHOICE~CHOICENUM, family = binomial, data = B_CHOICE)
summary(lm1)

# Generate values for Fig. 5: Predicted mean proportion of correct choices

# Create dataframe from 0 to 60
choicenumlm  <- data.frame (CHOICENUM = seq(0,60, length.out = 100)) 
# Create matrix of choice number
Xgc1 <- model.matrix(~CHOICENUM, data = B_CHOICE) 
#Create vector of model coefficients
coeff <- c(0.39529652, 0.01280739) 
# Calculate predicted mean proportion of correct choices
eta <- Xgc1 %*% coeff 
# Calculate standard errors
SE <- sqrt(diag(Xgc1 %*% vcov(lm1) %*% t(Xgc1))) 
#creates datafile with data from irid.dat (after reversing the link function)
write.csv(cbind(choicenumlm$CHOICENUM, eta, SE), "iridreg.csv") 

```

#### Unrewarded tests

Setting up subsets:

```{r message=FALSE}

# Generalized linear mixed model for unrewarded test conditions

B_TEST$BEEID <- as.factor(B_TEST$BEEID) #Treat Bee ID as factor
B_LEARN <- subset(B_TEST, TEST == "LEARNING") # Subset Learning test
B_TRANS <- subset(B_TEST, TEST == "TRANSFER") # Subset Transfer test
B_CONT <- subset(B_TEST, TEST == "CONTROL") # Subset Control test
B_CONF <- subset(B_TEST, TEST == "BLUE") # Subset  Conflict test 

```

##### Learning Test

```{r message=FALSE}

# Learning test model

lm_LEARN <- glmer(CHOICE~ 1 + (1|BEEID), family = binomial, data = B_LEARN) 
summary(lm_LEARN) 
(exp(1.386))/(1 + exp( 1.386)) # Mean proportion of correct choices
confint(lm_LEARN) # Calculate confidence intervals
(exp(0.9167736))/(1 + exp(0.9167736)) # Lower bound
(exp(2.010104))/(1 + exp(2.010104)) # Upper bound

```

##### Transfer Test

```{r message=FALSE}

# Transfer test model

lm_TRANS <- glmer(CHOICE~ 1 + (1|BEEID), family = binomial, data = B_TRANS) 
summary(lm_TRANS)  
(exp(1.6582))/(1 + exp( 1.6582)) # Mean proportion of correct choices
confint(lm_TRANS) # Calculate confidence intervals
(exp(1.152512))/(1 + exp(1.152512)) # Lower bound
(exp(2.2352976))/(1 + exp(2.2352976)) # Upper bound

```

##### Control Test

```{r message=FALSE}

# Control test model

lm_CONT <- glmer(CHOICE~ 1 + (1|BEEID), family = binomial, data = B_CONT) 
summary(lm_CONT)  
(exp(0.9445))/(1 + exp(0.9445)) # Mean proportion of correct choices
confint(lm_CONT) # Calculate confidence interval
(exp(0.514904))/(1 + exp(0.514904)) # Lower bound
(exp(1.4611194))/(1 + exp(1.4611194)) # Upper bound

```

##### Blue Test

```{r message=FALSE}

# Blue test model

lm_CONF <- glmer(CHOICE~ 1 + (1|BEEID), family = binomial, data = B_CONF) 
summary(lm_CONF)  
(exp(0.7082))/(1 + exp(0.7082)) # Mean proportion of correct choices
confint(lm_CONF) # Calculate confidence interval
(exp(0.2871733))/(1 + exp(0.2871733)) # Lower bound
(exp(1.1953020))/(1 + exp(1.1953020)) # Upper bound

```

##### Assumption checking 

```{r message=FALSE}

# Requires package DHaRMa 

simulationOutput_lm1 <- simulateResiduals(fittedModel = lm1, plot = T)
simulationOutput_LEARN <- simulateResiduals(fittedModel = lm_LEARN, plot = T)
simulationOutput_TRANS <- simulateResiduals(fittedModel = lm_TRANS, plot = T)
simulationOutput_CONT <- simulateResiduals(fittedModel = lm_CONT, plot = T)
simulationOutput_CONF <- simulateResiduals(fittedModel = lm_CONF, plot = T)
```


### Plot - Fig. 5 

Figure 5 was generated using Gnuplot using the 'Irid.dat' file and the following code:

```{r eval=FALSE}
reset
unset multiplot
set terminal pdfcairo size 14cm,14cm enhanced 
set terminal pdfcairo font "Helvetica,11"
set output 'iridgraph.pdf' #OUTPUT FILE
set style fill transparent solid 0.4
set style line 1 pt 7 ps 0.15 lw 1.5 lc rgb "black"
set style line 2 lc rgb "magenta" #medium
set style line 3 lc rgb "blue" #low
set style line 4 lc rgb "red" #high
set key bottom right noautotitle 
set xlabel "Choice number"
set ylabel "Mean proportion of correct choices"
set yrange [0:1]
set xrange [0:60]
set ytics 0,0.1,1
plot 'irid.dat' i 0 u 1:2:4 w filledc ls 3,  \
"" i 0 u 1:3 w l ls 1, "" i 1 u 2:1:3 with 
yerrorbars lc rgb("black") ps 0.3 linewidth 1
unset output
set terminal wxt
replot

```

# Supplementary materials

## Bee vision

### Models for the Iridescent stimulus

Supplementary Fig. S4 

Check the interactive plot below to see the results for each position of the light.

```{r fig.show='hide'}

# -------- position1 ----

### Visualize raw spectra
FigS4_p1Raw<-plot(IriData[,c(1, 2:5)],type = "s",labels.stack  =  
       c("20","15","12","10"),cex = 0.7)
### Create visual model
pos_1 <- vismodel(IriData[,c(1, 2:5)], visual  =  "apis", 
               achromatic = "l", illum = "D65", 
               qcatch = "Ei", bkg = BkgData$GB1_10, 
               vonkries = T, relative = F)
### visualize in hex space
hxpos1 <- colspace(pos_1, space = "hexagon")
FigS4_p1Vis<-plot(hxpos1)

# -------- position2 ----

### Visualize raw spectra
FigS4_p2Raw<-plot(IriData[,c(1, 6:11)],type = "s",labels.stack = 
       c("20","17","15","12","10","7"),cex = 0.7)
### Create visual model
pos_2 <- vismodel(IriData[,c(1,6:11)], visual = "apis",
               achromatic = "l", illum = "D65", 
               qcatch = "Ei", bkg = BkgData$GB1_10, 
               vonkries = T, relative = F)
### visualize in hex space
hxpos2 <- colspace(pos_2, space = "hexagon")
FigS4_p2Vis<-plot(hxpos2)


# -------- position3 ----

### Visualize raw spectra
FigS4_p3Raw<-plot(IriData[,c(1, 12:16)],type = "s",labels.stack = 
       c("20","15","12","10","7"),cex = 0.7)
### Create visual model
pos_3 <- vismodel(IriData[,c(1, 12:16)], 
               visual  =  "apis", achromatic = "l", 
               illum = "D65", qcatch = "Ei", 
               bkg = BkgData$GB1_10, vonkries = T, relative = F)
### visualize in hex space
hxpos3 <- colspace(pos_3, space = "hexagon")
FigS4_p3Vis<-plot(hxpos3)


# -------- position4 ----

### Visualize raw spectra
FigS4_p4Raw<-plot(IriData[,c(1, 17:21)],type = "s",labels.stack = 
       c("20","15","12","10","7"),cex = 0.7)
### Create visual model
pos_4 <- vismodel(IriData[,c(1, 17:21)], 
               visual = "apis", achromatic = "l", 
               illum = "D65", qcatch = "Ei",
               bkg = BkgData$GB1_10, vonkries = T, relative = F)
### visualize in hex space
hxpos4 <- colspace(pos_4, space = "hexagon")
FigS4_p4Vis<-plot(hxpos4)

# -------- position5 ----

### Visualize raw spectra
FigS4_p5Raw<-plot(IriData[,c(1,22:24)],type = "s",labels.stack =
       c("10","7","5"),cex = 0.7)
### Create visual model
pos_5 <- vismodel(IriData[,c(1,22:24)], 
               visual = "apis", achromatic = "l", 
               illum = "D65", qcatch = "Ei",
               bkg = BkgData$GB1_10, vonkries = T, relative = F)
### visualize in hex space
hxpos5 <- colspace(pos_5, space = "hexagon")
FigS4_p5Vis<-plot(hxpos5)

# -------- position6 ----

### Visualize raw spectra
FigS4_p6Raw<-plot(IriData[,c(1, 25:29)],type = "s",labels.stack  =  
       c("20","17","15","12","10"),cex = 0.7)
### Create visual model
pos_6 <- vismodel(IriData[,c(1, 25:29)], 
               visual = "apis", achromatic = "l", 
               illum = "D65", qcatch = "Ei", 
               bkg = BkgData$GB1_10, vonkries = T, relative = F)
### visualize in hex space
hxpos6 <- colspace(pos_6, space = "hexagon")
FigS4_p6Vis<-plot(hxpos6)

# -------- position7 ----

### Visualize raw spectra
FigS4_p7Raw<-plot(IriData[,c(1, 30:35)],type = "s",labels.stack = 
       c("20","17","15","12","10","7"),cex = 0.7)
### Create visual model
pos_7 <- vismodel(IriData[,c(1,30:35)], 
               visual = "apis", achromatic = "l",
               illum = "D65", qcatch = "Ei",
               bkg = BkgData$GB1_10, vonkries = T, relative = F)
### visualize in hex space
hxpos7 <- colspace(pos_7, space = "hexagon")
FigS4_p7Vis<-plot(hxpos7)

# -------- position8 ----

### Visualize raw spectra
FigS4_p8Raw<-plot(IriData[,c(1, 36:39)],type = "s",labels.stack =
       c("10","7","5", "x"),cex = 0.7)
### Create visual model
pos_8 <- vismodel(IriData[,c(1,36:39)], 
               visual  =  "apis", achromatic = "l", 
               illum = "D65", qcatch = "Ei", 
               bkg = BkgData$GB1_10, vonkries = T, relative = F)
### visualize in hex space
hxpos8 <- colspace(pos_8, space = "hexagon")
FigS4_p8Vis<-plot(hxpos8)

# -------- position9 ----

### Visualize raw spectra
FigS4_p9Raw<-plot(IriData[,c(1,40:45)],type = "s",labels.stack =
       c("20","17","15","12","10","7"),cex = 0.7)
### Create visual model
pos_9 <- vismodel(IriData[,c(1,40:45)], 
               visual = "apis", achromatic = "l",
               illum = "D65", qcatch = "Ei",
               bkg = BkgData$GB1_10, vonkries = T, relative = F)
### visualize in hex space
hxpos9 <- colspace(pos_9, space = "hexagon")
FigS4_p9Vis<-plot(hxpos9)

# -------- position10 ----

### Visualize raw spectra
FigS4_p10Raw<-plot(IriData[,c(1, 46:49)],type = "s",labels.stack =
       c("25","22","20","15"),cex = 0.7)
### Create visual model
pos_10 <- vismodel(IriData[,c(1, 46:49)], 
                visual = "apis", achromatic = "l",
                illum = "D65", qcatch = "Ei", 
                bkg = BkgData$GB1_10, vonkries = T, relative = F)
### visualize in hex space
hxpos10 <- colspace(pos_10, space = "hexagon")
FigS4_p10Vis<-plot(hxpos10)

# -------- position11 ----

### Visualize raw spectra
FigS4_p11Raw<-plot(IriData[,c(1, 50:52)],type = "s",labels.stack =
       c("12","10","7"),cex = 0.7)
### Create visual model
pos_11 <- vismodel(IriData[,c(1, 50:52)], 
                visual = "apis", achromatic = "l",
                illum = "D65", qcatch = "Ei", 
                bkg = BkgData$GB1_10, vonkries = T, relative = F)
### visualize in hex space
hxpos11 <- colspace(pos_11, space = "hexagon")
FigS4_p11Vis<-plot(hxpos11)


# -------- position12 ----

### Visualize raw spectra
FigS4_p12Raw<-plot(IriData[,c(1, 53:56)],type = "s",labels.stack =
       c("15","12","10","7"),cex = 0.7)
### Create visual model
pos_12 <- vismodel(IriData[,c(1, 53:56)],
                visual  =  "apis", achromatic = "l", 
                illum = "D65", qcatch = "Ei", 
                bkg = BkgData$GB1_10, vonkries = T, relative = F)
### visualize in hex space
hxpos12 <- colspace(pos_12, space = "hexagon")
FigS4_p12Vis<-plot(hxpos12)

# -------- position13 ----

### Visualize raw spectra
FigS4_p13Raw<-plot(IriData[,c(1, 57:61)],type = "s",labels.stack =
       c("20","17","15","12","10"),cex = 0.7)
### Create visual model
pos_13 <- vismodel(IriData[,c(1, 57:61)], 
                visual = "apis", achromatic = "l",
                illum = "D65", qcatch = "Ei",
                bkg = BkgData$GB1_10, vonkries = T, relative = F)
### visualize in hex space
hxpos13 <- colspace(pos_13, space = "hexagon")
FigS4_p13Vis<-plot(hxpos13)

# -------- position14 -----

### Visualize raw spectra
FigS4_p14Raw<-plot(IriData[,c(1,62:63)],type = "s",labels.stack = 
       c("20","17"),cex = 0.7)
### Create visual model
pos_14 <- vismodel(IriData[,c(1,62:63)], 
                visual = "apis", achromatic = "l", 
                illum = "D65", qcatch = "Ei",
                bkg = BkgData$GB1_10, vonkries = T, relative = F)
### visualize in hex space
hxpos14 <- colspace(pos_14, space = "hexagon")
FigS4_p14Vis<-plot(hxpos14)

# -------- position 15 ----

### Visualize raw spectra
FigS4_p15Raw<-plot(IriData[,c(1, 64:68)],type = "s",labels.stack =
       c("25","22","15","10","7"),cex = 0.7)
### Create visual model
pos_15 <- vismodel(IriData[,c(1, 64:68)], 
                visual = "apis", achromatic = "l",
                illum = "D65", qcatch = "Ei", 
                bkg = BkgData$GB1_10, vonkries = T, relative = F)
### visualize in hex space
hxpos15 <- colspace(pos_15, space = "hexagon")
FigS4_p15Vis<-plot(hxpos15)

```

#### Raw Spectra 

```{r echo=FALSE}

selectInput("Posit", "Choose the position of the light source",
            choices = c("P1","P2","P3","P4","P5",
                        "P6","P7","P8","P9","P10",
                        "P11","P12","P13","P14","P15"))


renderPlot({
 d <- input$Posit
 if (d == "P1") {
   plot(IriData[,c(1, 2:5)],type = "s",labels.stack  =  
       c("20","15","12","10"),cex = 0.7)
 } else if (d == "P2") {
   plot(IriData[,c(1, 6:11)],type = "s",labels.stack = 
       c("20","17","15","12","10","7"),cex = 0.7)
 } else if (d == "P3") {
   plot(IriData[,c(1, 12:16)],type = "s",labels.stack = 
       c("20","15","12","10","7"),cex = 0.7)
 } else if (d == "P4") {
   plot(IriData[,c(1, 17:21)],type = "s",labels.stack = 
       c("20","15","12","10","7"),cex = 0.7)
 } else if (d == "P5") {
   plot(IriData[,c(1,22:24)],type = "s",labels.stack =
       c("10","7","5"),cex = 0.7)
 } else if (d == "P6") {
   plot(IriData[,c(1, 25:29)],type = "s",labels.stack  =  
       c("20","17","15","12","10"),cex = 0.7)
 } else if (d == "P7") {
   plot(IriData[,c(1, 30:35)],type = "s",labels.stack = 
       c("20","17","15","12","10","7"),cex = 0.7)
 } else if (d == "P8") {
   plot(IriData[,c(1, 36:39)],type = "s",labels.stack =
       c("10","7","5", "2.5"),cex = 0.7)
 } else if (d == "P9") {
   plot(IriData[,c(1,40:45)],type = "s",labels.stack =
       c("20","17","15","12","10","7"),cex = 0.7)
 } else if (d == "P10") {
   plot(IriData[,c(1, 46:49)],type = "s",labels.stack =
       c("25","22","20","15"),cex = 0.7)
 } else if (d == "P11") {
   plot(IriData[,c(1, 50:52)],type = "s",labels.stack =
       c("12","10","7"),cex = 0.7)
 } else if (d == "P12") {
   plot(IriData[,c(1, 53:56)],type = "s",labels.stack =
       c("15","12","10","7"),cex = 0.7)
 } else if (d == "P13") {
   plot(IriData[,c(1, 57:61)],type = "s",labels.stack =
       c("20","17","15","12","10"),cex = 0.7)
 } else if (d == "P14") {
   plot(IriData[,c(1,62:63)],type = "s",labels.stack = 
       c("20","17"),cex = 0.7)
 } else if (d == "P15") {
   plot(IriData[,c(1, 64:68)],type = "s",labels.stack =
       c("25","22","15","10","7"),cex = 0.7)
 } } )


```

#### Correspondent Hex Models

```{r echo =FALSE, out.width = "120%"}

selectInput("Position", "Choose the position of the light source",
            choices = c("P1","P2","P3", "P4", "P5",
                        "P6","P7","P8","P9","P10",
                        "P11","P12","P13","P14","P15"))


renderPlot({
 d <- input$Position
 if (d == "P1") {
   plot(hxpos1)
 } else if (d == "P2") {
   plot(hxpos2)
 } else if (d == "P3") {
   plot(hxpos3)
 } else if (d == "P4") {
   plot(hxpos4)
 } else if (d == "P5") {
   plot(hxpos5)
 } else if (d == "P6") {
   plot(hxpos6)
 } else if (d == "P7") {
   plot(hxpos7)
 } else if (d == "P8") {
   plot(hxpos8)
 } else if (d == "P9") {
   plot(hxpos9)
 } else if (d == "P10") {
   plot(hxpos10)
 } else if (d == "P11") {
   plot(hxpos11)
 } else if (d == "P12") {
   plot(hxpos12)
 } else if (d == "P13") {
   plot(hxpos13)
 } else if (d == "P14") {
   plot(hxpos14)
 } else if (d == "P15") {
   plot(hxpos15) 
 } } )


```

#### As presented in FigS4 


```{r}

# -------- all positions (as presented in the figure) ----

### Create visual model
pos_all <- vismodel(IriData[,c(1, 2:68)], 
                visual = "apis", achromatic = "l",
                illum = "D65", qcatch = "Ei", 
                bkg = BkgData$GB1_10, # grey background
                vonkries = T, relative = F)
### visualize in hex space
hxposall <- colspace(pos_all, space = "hexagon")
plot(hxposall)

```

### Models for the Distractors

Supplementary Fig. S4/S5 

```{r fig.show='hide', results='hide'}

# -------- distractor1 ----
spec2rgb(DisData[,c(1,2:4)])
bee_d1 <- vismodel(DisData[,c(1,2:4)], visual = "apis", 
                achromatic = "l", illum = "D65",
                qcatch = "Ei", bkg = BkgData$GB1_10, 
                vonkries = T, relative = F)
hsd1 <- colspace(bee_d1, space = "hexagon")
plot(hsd1,col = c("#A0B616FF","#FFD113FF","#7CB8C4FF"),cex = 1.5)

# -------- distractor2 ----
spec2rgb(DisData[,c(1,5:8)])
bee_d2 <- vismodel(DisData[,c(1,5:8)], visual = "apis", 
                achromatic = "l", illum = "D65", 
                qcatch = "Ei", bkg = BkgData$GB1_10, 
                vonkries = T, relative = F)
hsd2 <- colspace(bee_d2, space = "hexagon")
plot(hsd2,col = c("#8CA400FF", "#5995D7FF", "#7F97DBFF", "#A3D1E8FF"),cex = 1.5)

# -------- distractor3 ----
spec2rgb(DisData[,c(1,9:11)])
bee_d3 <- vismodel(DisData[,c(1,9:11)], visual = "apis", 
                achromatic = "l", illum = "D65", 
                qcatch = "Ei", bkg = BkgData$GB1_10, 
                vonkries = T, relative = F)
hsd3 <- colspace(bee_d3, space = "hexagon")
plot(hsd3,cex = 1.5,col = c("#C86271FF", "#FFD600FF", "#A0AF3AFF" ))

# -------- distractor4 ----
spec2rgb(DisData[,c(1,12:14)])
bee_d4 <- vismodel(DisData[,c(1,12:14)], visual = "apis", 
                achromatic = "l", illum = "D65", 
                qcatch = "Ei", bkg = BkgData$GB1_10, 
                vonkries = T, relative = F)
hsd4 <- colspace(bee_d4, space = "hexagon")
plot(hsd4,cex = 1.5,col = c("#00A3B2FF", "#009596FF", "#6FAC87FF" ))

# -------- distractor5 ----
spec2rgb(DisData[,c(1,15:17)])
bee_d5 <- vismodel(DisData[,c(1,15:17)], visual = "apis", 
                achromatic = "l", illum = "D65", 
                qcatch = "Ei", bkg = BkgData$GB1_10, 
                vonkries = T, relative = F)
hsd5 <- colspace(bee_d5, space = "hexagon")
plot(hsd5,cex = 1.5,col = c("#88A539FF" ,"#5BAFB9FF", "#EEBBD9FF" ))

# -------- distractor6 ----
spec2rgb(DisData[,c(1,18:20)])
bee_d6 <- vismodel(DisData[,c(1,18:20)], visual = "apis", 
                achromatic = "l", illum = "D65", 
                qcatch = "Ei", bkg = BkgData$GB1_10, 
                vonkries = T, relative = F)
hsd6 <- colspace(bee_d6, space = "hexagon")
plot(hsd6,cex = 1.5,col = c("#FDD184FF", "#C8C8A1FF", "#D59D9AFF"))

# -------- distractor7 ----
spec2rgb(DisData[,c(1,21:23)])
bee_d7 <- vismodel(DisData[,c(1,21:23)], visual = "apis", 
                achromatic = "l", illum = "D65", 
                qcatch = "Ei", bkg = BkgData$GB1_10, 
                vonkries = T, relative = F)
hsd7 <- colspace(bee_d7, space = "hexagon")
plot(hsd7,cex = 1.5,col = c("#0062AEFF", "#777E8EFF", "#E08B9BFF" ))

# -------- distractor8 ----
spec2rgb(DisData[,c(1,24:27)])
bee_d8 <- vismodel(DisData[,c(1,24:27)], visual = "apis", 
                achromatic = "l", illum = "D65", 
                qcatch = "Ei", bkg = BkgData$GB1_10, 
                vonkries = T, relative = F)
hsd8 <- colspace(bee_d8, space = "hexagon")
plot(hsd8,cex = 1.5,col = c("#78991BFF", "#44B6DAFF" ,
                        "#0081B5FF" ,"#1E78BEFF" ))

# -------- distractor9 ----
spec2rgb(DisData[,c(1,28:31)])
bee_d9 <- vismodel(DisData[,c(1,28:31)], visual = "apis", 
                achromatic = "l", illum = "D65", 
                qcatch = "Ei", bkg = BkgData$GB1_10, 
                vonkries = T, relative = F)
hsd9 <- colspace(bee_d9, space = "hexagon")
plot(hsd9,cex = 1.5,col = c("#2069BAFF", "#77AE5CFF", 
                        "#83B9CDFF", "#C87892FF" ))

# -------- distractor10 ----
spec2rgb(DisData[,c(1,32:35)])
bee_d10 <- vismodel(DisData[,c(1,32:35)], visual = "apis", 
                 achromatic = "l", illum = "D65", 
                 qcatch = "Ei", bkg = BkgData$GB1_10, 
                 vonkries = T, relative = F)
hsd10 <- colspace(bee_d10, space = "hexagon")
plot(hsd10,cex = 1.5,col = c("#FFD31BFF", "#BCB227FF" ,
                         "#E398A0FF" ,"#D286A3FF" ))

# -------- distractor11 ----
spec2rgb(DisData[,c(1,36:40)])
bee_d11 <- vismodel(DisData[,c(1,36:40)], visual = "apis", 
                 achromatic = "l", illum = "D65", 
                 qcatch = "Ei", bkg = BkgData$GB1_10, 
                 vonkries = T, relative = F)
hsd11 <- colspace(bee_d11, space = "hexagon")
plot(hsd11,cex = 1.5,col = c("#F1BF20FF", "#ECA3ABFF", "#65B3BDFF", 
                         "#9DB8F0FF" ,"#82A320FF" ))

# -------- distractor12 ----
spec2rgb(DisData[,c(1,41:44)])
bee_d12 <- vismodel(DisData[,c(1,41:44)], visual = "apis", 
                 achromatic = "l", illum = "D65", 
                 qcatch = "Ei", bkg = BkgData$GB1_10, 
                 vonkries = T, relative = F)
hsd12 <- colspace(bee_d12, space = "hexagon")
plot(hsd12,cex = 1.5,col = c("#8CA5ADFF", "#0095B4FF", 
                         "#C7AA89FF" ,"#DD83A4FF" ))

# -------- distractor13 ----
spec2rgb(DisData[,c(1,45:48)])
bee_d13 <- vismodel(DisData[,c(1,45:48)], visual = "apis",
                 achromatic = "l", illum = "D65", 
                 qcatch = "Ei", bkg = BkgData$GB1_10, 
                 vonkries  = T, relative = F)
hsd13 <- colspace(bee_d13, space = "hexagon")
plot(hsd13,cex = 1.5,col = c("#CE4852FF" ,"#7DA718FF" ,
                         "#537162FF", "#DE8F36FF" ))


```

#### Hex Models Results

```{r echo =FALSE, out.width = "120%"}

selectInput("Position2", "Choose the position of the light source",
            choices = c("P1","P2","P3", "P4", "P5",
                        "P6","P7","P8","P9","P10",
                        "P11","P12","P13","P14","P15"))


renderPlot({
 d <- input$Position2
 if (d == "P1") {
   plot(hsd1)
 } else if (d == "P2") {
   plot(hsd2)
 } else if (d == "P3") {
   plot(hsd3)
 } else if (d == "P4") {
   plot(hsd4)
 } else if (d == "P5") {
   plot(hsd5)
 } else if (d == "P6") {
   plot(hsd6)
 } else if (d == "P7") {
   plot(hsd7)
 } else if (d == "P8") {
   plot(hsd8)
 } else if (d == "P9") {
   plot(hsd9)
 } else if (d == "P10") {
   plot(hsd10)
 } else if (d == "P11") {
   plot(hsd11)
 } else if (d == "P12") {
   plot(hsd12)
 } else if (d == "P13") {
   plot(hsd13)
 } else if (d == "P14") {
   plot(hsd14)
 } else if (d == "P15") {
   plot(hsd15) 
 } } )


```


## Stimulus

### Spectral Characterization

#### Illumination = 1 mm spot

```{r}

IriPoint2 <-
  IriPoint %>% 
  select (c(1:5,10:13, 18:21))

IriPoint3 <- aggspec(IriPoint2, by = 4, FUN = mean)

ForIrP2 <- 
  IriPoint3 %>% 
  gather (Angle, Reflectance, - wl) %>% 
  mutate (halfSpan = as.factor(substr(Angle, 4,5))) %>% 
  select (-Angle)

ggplot (ForIrP2, aes(wl, Reflectance)) +
  geom_line(aes(color=halfSpan), size=0.8) +
  theme_bw() +
  scale_colour_manual(values=c("#e59f16","#1973b5","#40748F"))+
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank())+
  theme(legend.position = "none") +
  theme(axis.title.x = element_text(vjust=-2),
        axis.title.y = element_text(vjust=+2.5))+
  ylab("Reflectance (%)")+
  xlab("Wavelength (nm)")

```

#### Illumination = 1 cm spot

Position 3 as an example

```{r}

ForP03 <- 
  IriData %>% 
  select (wl, contains ("P03")) %>% 
  gather (Pos, Reflectance, - wl) %>% 
  mutate (Angle = substr(Pos,5,6)) %>% 
  filter(Angle != "07" & 
         Angle != "12")

ggplot (ForP03, aes(wl, Reflectance)) +
  geom_line(aes(color=Angle), size=0.8) +
  theme_bw() +
  scale_colour_manual(values=c("#e59f16","#1fa072","#1973b5"))+
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank())+
  theme(legend.position = "none") +
  theme(axis.title.x = element_text(vjust=-2),
        axis.title.y = element_text(vjust=+2.5))+
  ylab("Reflectance (%)")+
  xlab("Wavelength (nm)")
  
  

```


#### Visualization of the blue stimulus Fig. S6
```{r}

plot(BlueData[,c(1, 2)], cex = 0.7)
```

